A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-08-12 doc/large_strain.tex
Update affiliations

\ifijnme
\author[1]{Denis Davydov*}
\author[1]{Jean-Paul Pelteret}
\author[2]{Daniel Arndt}
\author[3]{Martin Kronbichler}
\author[1,4]{Paul Steinmann}

@@

\address[3]{\orgdiv{Institute for Computational Mechanics}, \orgname{Technical University of Munich}, \orgaddress{\country{Germany}}}

\address[4]{\orgdiv{Glasgow Computational Engineering Center (GCEC)}, \orgname{University of Glasgow}, \orgaddress{\country{United Kingdom}}}

@@

  \author[a]{Denis Davydov\corref{cor}}
  \ead{denis.davydov@fau.de}

@@

  \author[b]{Daniel Arndt}
  \ead{daniel.arndt@iwr.uni-heidelberg.de}

  \author[a,c]{Paul Steinmann}
  \ead{paul.steinmann@fau.de}

@@

  \address[c]{Glasgow Computational Engineering Center (GCEC),
      University of Glasgow, G12 8QQ Glasgow, United Kingdom
  }
\fi
  \begin{abstract}[Summary]
    {{\color{red}This work investigates matrix-free algorithms for problems in quasi-static finite-strain hyperelasticity. Iterative solvers with matrix-free operator evaluation have emerged as
an attractive alternative to sparse matrices in the fluid dynamics and wave
propagation communities because they significantly reduce the memory traffic,
the limiting factor in classical finite element solvers.
    Specifically, we study different matrix-free realizations of the finite element tangent operator, and determine whether generalized methods of incorporating complex constitutive behavior might be feasible.}
    In order to improve the convergence behavior of iterative solvers, we also propose a method by which to construct level tangent operators
    and employ them to define a geometric multigrid preconditioner.
    The performance of the matrix-free operator and the geometric multigrid preconditioner is compared to the matrix-based implementation with an algebraic multigrid preconditioner on a single node for a representative numerical example of a heterogeneous hyperelastic material in two and three dimensions.
    We {\color{red}find} that matrix-free methods for finite-strain solid mechanics are very promising, {\color{red}outperforming linear matrix-based schemes by two to five times}, and that is it possible to develop numerically efficient implementations that are independent of the hyperelastic constitutive law.}
  \end{abstract}

>>>>

\ifijnme
\author[1]{Denis Davydov*}
\author[1]{Jean-Paul Pelteret}
\author[2,3]{Daniel Arndt}
\author[4]{Martin Kronbichler}
\author[1,5]{Paul Steinmann}

@@

\address[3]{\orgdiv{Computational Engineering and Energy Sciences Group},
         \orgname{Oak Ridge National Laboratory}, \orgaddress{Oak Ridge, TN, USA}}

\address[4]{\orgdiv{Institute for Computational Mechanics}, \orgname{Technical University of Munich}, \orgaddress{\country{Germany}}}

\address[5]{\orgdiv{Glasgow Computational Engineering Center (GCEC)}, \orgname{University of Glasgow}, \orgaddress{\country{United Kingdom}}}

@@

\else
 \author[a]{Denis Davydov\corref{cor}}
  \ead{denis.davydov@fau.de}

@@

  \author[b,c]{Daniel Arndt
   \footnotetext{%
   This manuscript has been authored by UT-Battelle, LLC under Contract No.
   DE-AC05-00OR22725 with the U.S. Department of Energy. The United States Government
   retains and the publisher, by accepting the article for publication, acknowledges
   that the United States Government retains a non-exclusive, paid-up, irrevocable,
   worldwide license to publish or reproduce the published form of this manuscript,
   or allow others to do so, for United States Government purposes. The Department
   of Energy will provide public access to these results of federally sponsored
   research in accordance with the DOE Public Access Plan
   (http://energy.gov/downloads/doe-public-access-plan).}}
  \ead{arndtd@ornl.gov}

  \author[d]{Martin Kronbichler}
  \ead{kronbichler@lnm.mw.tum.de}

  \author[a,e]{Paul Steinmann}
  \ead{paul.steinmann@fau.de}

@@

  \address[c]{Computational Engineering and Energy Sciences Group,
         Oak Ridge National Laboratory;
         Oak Ridge, TN, USA}

   \address[d]{Institute for Computational Mechanics, Technical University of Munich; Garching, Germany}

  \address[e]{Glasgow Computational Engineering Center (GCEC),
      University of Glasgow, G12 8QQ Glasgow, United Kingdom
  }
\fi
  \begin{abstract}[Summary]
    {{\color{red}This work investigates matrix-free algorithms for problems in quasi-static finite-strain hyperelasticity. Iterative solvers with matrix-free operator evaluation have emerged as
an attractive alternative to sparse matrices in the fluid dynamics and wave
propagation communities because they significantly reduce the memory traffic,
the limiting factor in classical finite element solvers.
    Specifically, we study different matrix-free realizations of the finite element tangent operator, and determine whether generalized methods of incorporating complex constitutive behavior might be feasible.}
    In order to improve the convergence behavior of iterative solvers, we also propose a method by which to construct level tangent operators
    and employ them to define a geometric multigrid preconditioner.
    The performance of the matrix-free operator and the geometric multigrid preconditioner is compared to the matrix-based implementation with an algebraic multigrid preconditioner on a single node for a representative numerical example of a heterogeneous hyperelastic material in two and three dimensions.
    We {\color{red}find} that matrix-free methods for finite-strain solid mechanics are very promising, {\color{red}outperforming linear matrix-based schemes by two to five times}, and that is it possible to develop numerically efficient implementations that are independent of the hyperelastic constitutive law.}\footnotetext{%
   This manuscript has been authored by UT-Battelle, LLC under Contract No.
   DE-AC05-00OR22725 with the U.S. Department of Energy. The United States Government
   retains and the publisher, by accepting the article for publication, acknowledges
   that the United States Government retains a non-exclusive, paid-up, irrevocable,
   worldwide license to publish or reproduce the published form of this manuscript,
   or allow others to do so, for United States Government purposes. The Department
   of Energy will provide public access to these results of federally sponsored
   research in accordance with the DOE Public Access Plan
   (http://energy.gov/downloads/doe-public-access-plan).}
  \end{abstract}
